The ChEMBL database as Linked Open Data

### 2012-05-01 article.tex
Clarified 'free'. Being first author, the use has to be more exact than normally

ChemSpider~\cite{Pence2010} is a free online database provided by RSC. It contains over 26 million unique
chemical compounds aggregated from over 400 data sources as well as chemical data extracted
from RSC scientific articles and databases. Since its inception, efforts have been made to
utilize it as both a deposition platform for the community to contribute novel data, as
well as a platform for annotation and curation for existing data. Studies have shown that there are data
quality issues in many of the public compound databases~\cite{Williams2011}. ChemSpider has become a
valuable resource for curated data, especially chemical-compound name mappings. ChemSpider
is presently providing the chemical structure, substructure and similarity searching services 
underpinning the Open PHACTS semantic web project~\cite{Williams2012}. Specific chemical data 
sources containing data mappings between ChemSpider identifiers (CSIDs) and the original data 
source identifiers have been provided to the triple store, together with chemical identifiers 
including validated chemical names (systematic, generic and trivial), SMILES () and InChIs (). 
The data mappings between the CSIDs and ChEMBL IDs are released to the 
community under the Creative Common Attribution-Share Alike license (CC-BY-SA 3.0). Attribution 
should be made to the original ChEMBL database, Open PHACTS, and ChemSpider.

>>>>

ChemSpider~\cite{Pence2010} is a freely accessible, online database provided by RSC. It contains over 26 million unique
chemical compounds aggregated from over 400 data sources as well as chemical data extracted
from RSC scientific articles and databases. Since its inception, efforts have been made to
utilize it as both a deposition platform for the community to contribute novel data, as
well as a platform for annotation and curation for existing data. Studies have shown that there are data
quality issues in many of the public compound databases~\cite{Williams2011}. ChemSpider has become a
valuable resource for curated data, especially chemical-compound name mappings. ChemSpider
is presently providing the chemical structure, substructure and similarity searching services 
underpinning the Open PHACTS semantic web project~\cite{Williams2012}. Specific chemical data 
sources containing data mappings between ChemSpider identifiers (CSIDs) and the original data 
source identifiers have been provided to the triple store, together with chemical identifiers 
including validated chemical names (systematic, generic and trivial), SMILES, and InChIs. 
The data mappings between the CSIDs and ChEMBL IDs are released to the 
community under the Creative Common Attribution-Share Alike license (CC-BY-SA 3.0). Attribution 
should be made to the original ChEMBL database, Open PHACTS, and ChemSpider.
